Personality and political beliefs across the lifespan

### 2019-11-27 scripts/manuscript.Rmd

apa_table(tidy_table, 
            caption = "Mean Personality Trait Scores Across the Lifespan",
          col_spanners = list(`Age Group` = c(2, 6)),
          note = "Personality trait scores reported on a 1-7 scale."
)
```

@@

ggplot(tidy, aes(x = age, y = conservatism_score, color = conservatism_type)) +
  geom_smooth(se=FALSE, method = "lm")+
  scale_color_viridis_d() +
  labs(title = "Conservatism across the lifespan (adults aged 20-68)", subtitle = "Difference in Economic and Social Conservatism by Gender",
       x= "Age", y = "Conservatism Score (higher = more conservative)",
       color = "Conservatism Type")+
  theme_minimal()+
  facet_wrap(~gender)
```

>>>>

apa_table(tidy_table, 
            caption = "Mean Personality Trait Scores Across the Lifespan",
          col_spanners = list(`Age Group` = c(2, 6)),
          note = "Personality trait scores reported on a 1-7 scale."
)

#This table is helpful and conveys a lot of information in a very clear format. 
```

@@

ggplot(tidy, aes(x = age, y = conservatism_score, color = conservatism_type)) +
  geom_smooth(se=FALSE, method = "lm")+
  scale_color_viridis_d() +
  labs(title = "Conservatism across the lifespan (adults aged 20-68)", subtitle = "Difference in Economic and Social Conservatism by Gender",
       x= "Age", y = "Conservatism Score (higher = more conservative)",
       color = "Conservatism Type")+
  theme_minimal()+
  facet_wrap(~gender)

#You could use this same plot and facet wrap by ethnicity instead of gender. 
```
